Pillar 1 - Sequential Pattern Mining

### 2019-02-12 Pillar 1 - Sequential Pattern Mining.Rmd
include summary at type level

@@

rm(provide_statistics, statistics_student, statistics_course, statistics_cluster,
     statistics_concentration, statistics_year, statistics_level)
```

>>>>

# Type level
statistics_type <- d_transcript %>%
  inner_join(d_course, by = "Course ID") %>%
  filter(!is.na(Type)) %>%
  group_by(Type) %>%
  provide_statistics()

@@

#rm(provide_statistics, statistics_student, statistics_course, statistics_cluster,
#     statistics_concentration, statistics_year, statistics_level)
```
